Type Refinements for the Working Class

### 2015-11-22 paper.tex
improve rule labels
Make the definition of functional refinement more precise

Then, we say that $\phi$ \emph{globally refines} $\tau$ (written
$\GRefines{\phi}{\tau}$) when for all $\Upsilon$, we have
$\Refines{\Upsilon}{\phi}{\tau}$.

@@

\newcommand\PRefinesCtxNil{\leftidx{^\parallel}{\!\!\sqsubset}{^\star_{\mathtt{nil}}}}
\newcommand\PRefinesCtxSnoc{\leftidx{^\parallel}{\!\!\sqsubset}{^\star_{\mathtt{snoc}}}}

@@

@@

\paragraph{Case} $\DefPRefinesCtxNil{\Upsilon}$.
\[
  \infer{
    \HEqRefines{\Upsilon}{\cdot}{\phi}{\psi}{\tau}
  }{
    \EqRefines{\Upsilon}{\phi}{\psi}{\tau}
  }
\]

@@

\begin{gather*}
  \infer{
    \HEqRefines{\Upsilon}{\Psi,x:\chi}{\phi}{\psi}{\tau}
  }{
    \HPGenJ{\Upsilon}{\Gamma}{\MV{m},\MV{n}:\sigma}{
      \HypJ{
        \HEqRefines{\Upsilon}{\Psi}{
          \Subst{\MV{m}}{x}{\phi}
        }{
          \Subst{\MV{n}}{x}{\psi}
        }{\tau}
      }{
        \HRMemEq{\Upsilon}{\Psi}{\MV{n}}{\MV{n}}{\chi}
      }
    }
  }
\end{gather*}

\todo[inline]{%
  Is the above a correct rule? I think that it might be good to be explicit
  here rather than using the hypothetico-general judgment. In fact, if we are
  explicit about everything, we can get away with not even explaining the
  higher-order judgments.
}

>>>>

Then, we say that $\phi$ \emph{globally refines} $\tau$ (written
$\GRefines{\phi}{\tau}$) when we have $\Refines{\cdot}{\phi}{\tau}$.
Furthermore, when $\Refines{\Upsilon}{\phi}{\tau}$, for any renaming
\begin{tikzcd}[cramped]
  \IMode{\Upsilon}\arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd}
we can define a new refinement $\phi\rho$ such that
$\Refines{\Upsilon'}{\phi\rho}{\tau}$ in the obvious way.

@@

\newcommand\PRefinesCtxNil{\sqsubset^\star_{\mathtt{nil}}}
\newcommand\PRefinesCtxSnoc{\sqsubset^\star_{\mathtt{snoc}}}
\newcommand\PFunRefNil{\vDash^\sqsubset_{\mathtt{nil}}}
\newcommand\PFunRefSnoc{\vDash^\sqsubset_{\mathtt{snoc}}}

@@

For a context refinement $\PRefinesCtx{\Upsilon}{\Psi}{\Gamma}$ and a renaming
\begin{tikzcd}[cramped]
  \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd},
we can define a new context refinement
$\PRefinesCtx{\Upsilon'}{\Psi\rho}{\Gamma}$ by applying $\rho$ pointwise at
each of the sort refinements in the context.

@@

\paragraph{Case} $\DefPRefinesCtxNil{\Upsilon}$.
\[
  \infer[\PFunRefNil]{
    \HEqRefines{\Upsilon}{\cdot}{\phi}{\psi}{\tau}
  }{
    \EqRefines{\Upsilon}{\phi}{\psi}{\tau}
  }
\]

@@

\begin{quote}
  To know $\HEqRefines{\Upsilon}{\Psi,x:\chi}{\phi}{\psi}{\tau}$ is to know, for any renaming
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd}
  and closed terms $\Member{M,N}{\Exprs_\sigma(\Upsilon')}$, that from
  $\HRMemEq{\Upsilon}{\Psi\rho}{M}{N}{\chi\rho}$, you can conclude
  $\HRMemEq{\Upsilon}{\Psi\rho}{\Subst{M}{x}{\phi\rho}}{\Subst{N}{x}{\psi\rho}}{\tau}$.

\end{quote}
